### 2016-01-06 pdocs/thesis/introduction.tex
pdocs

@@

Physics engines is active research area on many research and industry areas.
Especially gaming and movie industry are powerful drivers.
Robotics and solid mechanics are typical research areas that use physics engines.

@@

@@

This work opens wide area of further work of combining structural analysis and plasticity with physics engines.
Few examples are shown in sections~\ref{sec:results} and \ref{subsec:futureWork}

>>>>

This work tries to invite structural engineers to take active part in development of more realistic physis engines.
Current computer systems provide enough computing performance and efficient algorithms so collision detection and 
rigid body dynamics can be handled in real time in most scenarios.
Soft body dynamics in which  object are deformable is in many cases still too complicated for real time applications.
Finite element method will probably replace other methods by providing general solution at some time but not in very near future.
In this work focus is on method where rigid bodies are connected by constraints.

@@

Physics engines is active research area on many research and industry areas.
Especially gaming and movie industry are powerful drivers.
Robotics is typical research areas that uses physics engines.

@@

\cite{cornell.cs3152}

@@

This work opens wide area of further work of combining structural analysis and plasticity with physics engines.
Few examples are shown in sections~\ref{sec:results} and possible areas of further work are discussed in \ref{subsec:futureWork}.
